A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-01-20 03_Prep_data.Rmd
Save full dataset to object before slimming

```{r simplifyData}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "control",
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          id = row_number(),
          vi = yield_error,
          n = replicates) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype,
      spray_management,
      fungicide_ai,
      grain_yield.t.ha.,
      yield_gain,
      vi,
      vi2,
      n,
      id)
```

```{r saveData_PrepD}
save(PM_MB_dat, file = here("cache/PrepData.Rdata"))
```

>>>>

```{r simplifyData}
PM_MB_dat_full <- PM_MB_dat

PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "control",
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          id = row_number(),
          vi = yield_error,
          n = replicates) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype,
      spray_management,
      fungicide_ai,
      grain_yield.t.ha.,
      yield_gain,
      vi,
      vi2,
      n,
      id)
```

```{r saveData_PrepD}
save(PM_MB_dat, PM_MB_dat_full, file = here("cache/PrepData.Rdata"))
```
